---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# heck

<!-- badges: start -->
[![R-CMD-check](https://github.com/DyfanJones/heck/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/DyfanJones/heck/actions/workflows/R-CMD-check.yaml)
[![heck status badge](https://dyfanjones.r-universe.dev/badges/heck)](https://dyfanjones.r-universe.dev/heck)
[![Codecov test coverage](https://codecov.io/gh/DyfanJones/heck/branch/master/graph/badge.svg)](https://app.codecov.io/gh/DyfanJones/heck?branch=master)
<!-- badges: end -->

This repository was developed from the excellent tutorial https://extendr.github.io/user-guide/heckin-case-converter.html. This package is a thin wrapper around the rust crate [heck](https://crates.io/crates/heck) allowing `R` to convert character vectors to specific cases super fast.

## Installation

You can install the development version of `heck` like so:

r-universe:
```r
install.packages("heck", repos = c("https://dyfanjones.r-universe.dev", "https://cran.r-project.org"))
```

Github:
``` r
remotes::install_github("dyfanjones/heck")
```

## Code of Conduct
  
Please note that the `R` `heck` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Example

```{r example}
library(heck)


x <- "Demo String"

to_kebab_case(x)

to_lower_camel_case(x)

to_upper_camel_case(x)

to_pascal_case(x)

to_snake_case(x)

to_snek_case(x)

to_title_case(x)

to_train_case(x)

to_shouty_kebab_case(x)

to_shouty_snake_case(x)
```
